A thermodynamic view of dusty protoplanetary disks

### 2017-07-14 paper.tex
tiny intro edits (this paper is organized...), remove repeated text in SI section

Under these two approximations of strong drag and isothermal gas, we show that the equations of 
 dusty gas dynamics are equivalent to that of nearly adiabatic (i.e. slowly cooling) gas
dynamics without dust (Fig. \ref{concept_chart}).  The basis of the analogy is that the entrainment 
of tightly-coupled dust particles in gas flows is similar to the advection
of entropy in an adiabatic fluid. %We show that the   
%effective entropy of isothermal dusty gas scales with its gas
%fraction.  %AY: too technical for introduction.
Finite dust-gas drag act as effective heating/cooling: the relative
drift between dust and gas causes a fluid parcel to exchange dust
particles with its surroundings; an effect similar to heat exchange
between a gas parcel and its surroundings.   Needless to say the effective heating term must have a 
specific form, which we derive, for the equivalency to hold.

@@

This paper is organized as follows. 
In \S\ref{grow_osc} 
we describe a key insight of our study, that pressure (i.e.\ ``PdV") work explains the basis of several instabilities, including SI and VSI, in terms of
pressure-density phase lags.    
We develop our formalism in \S\ref{setup} by transforming the
two fluid equations of a tightly-coupled dusty gas into single fluid
hydrodynamic equations with a special cooling function.  Here we also
define the effective entropy and buoyancy of our model fluid. 
%We derive equilibrium solutions in \S\ref{eqm}, which we use in our
%explicit stability calculations.
In \S\ref{limits} we analyze the general stability properties of dusty
disks. We then move onto explicit stability analyses in
\S\ref{linear_problem}, were we show that dusty edges are unstable,
and revisit the SGI and SI in the tight
coupling regime. In \S\ref{results} we
extend the VSI to dusty disks. We   
discuss future applications of the dusty/adiabatic gas equivalence in 
\S\ref{discussion} before summarizing in \S\ref{summary}.

>>>>

Under these two approximations of strong drag and isothermal gas, we show that the equations of 
 dusty gas dynamics are equivalent to that of nearly adiabatic (i.e. slowly cooling) gas
dynamics without dust, see Fig.~\ref{concept_chart}.  The basis of the analogy is that the entrainment 
of tightly-coupled dust particles in gas flows is similar to the advection
of entropy in an adiabatic fluid. %We show that the   
%effective entropy of isothermal dusty gas scales with its gas
%fraction.  %AY: too technical for introduction.
Finite dust-gas drag act as effective heating/cooling: the relative
drift between dust and gas causes a fluid parcel to exchange dust
particles with its surroundings; an effect similar to heat exchange
between a gas parcel and its surroundings.   Needless to say the effective heating term must have a 
specific form, which we derive, for the equivalency to hold.

@@

This paper is organized as follows. 
In \S\ref{grow_osc} 
we describe a key insight of our study, that pressure (i.e.\ ``PdV") work explains the basis of several instabilities, including SI and VSI, in terms of
pressure-density phase lags.    
We develop our formalism in \S\ref{setup} by transforming the
two fluid equations of a tightly-coupled dusty gas into single fluid
hydrodynamic equations with a special cooling function.  Here we also
define the effective entropy and buoyancy of our model fluid. 
%We derive equilibrium solutions in \S\ref{eqm}, which we use in our
%explicit stability calculations.
In \S\ref{limits} we discuss general stability properties of dusty
disks. We then analyze explicit disk models 
\S\ref{linear_problem}, were we show that dusty edges are unstable,
and revisit the SGI and SI in the tight 
coupling regime. In \S\ref{results} we 
extend the VSI to dusty disks. We   
discuss future applications of the dusty/adiabatic gas equivalence in 
\S\ref{discussion} before summarizing in \S\ref{summary}.
